Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-26 GWLDCII.tex
oops didn't save
some changes made before going on vacation

Since each propagator is removed by the algorithm after it contributes, each propagator contributed exactly once to $I_i$, making the above ordering well defined.
Note that different $I_*$ impose different orderings on the propagators. Furthermore, Lemma \ref{lem no fourth vertex} shows that this ordering respects the ordering of vertices in $I_i$. That is, $I_i(p_j) <_i I_i(p_l)$ for all $j <l$.

@@

\begin{rmk} \label{clockwise ordering rem}
When $p$ contributes $I_i(p) = a$, it must be the clockwise-most propagator amongst those not yet assigned that is supported on $a$ i.e. any propagator assigned later that is supported on $a$ must be inside $(p, <_{a-1})$.
\end{rmk} \sanote{We use this fact at least twice below}

@@

With this setup, if we can find a vertex $\ell$ (with \st{$\ell <_i i$ and $\ell <_m m$} {\color{violet} $i <_i \ell$ and $m <_m \ell$?}) such that the \emph{configuration} of propagators ending in the interval \st{$(j-1, \ldots, \ell+1)$} {\color{violet}$[j, l]$} is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive). See Figure~\ref{fig:locally identical} for an illustration of this.

@@

With that in mind, we are ready to begin proving properties of the algorithm. We first show that the algorithm for $I_i$ can never reach the final vertex (in the $<_i$ order) in a propagator's support without having already assigned that propagator; in particular, this guarantees that the construction of $I_i$ always terminates in fewer than $n$ steps.

\begin{lem}\label{lem no fourth vertex}
Let $W$ be an admissible Wilson loop diagram containing at least one propagator. For any $i \in [n]$ and for any $p \in \cP$, $I_i(p)$ is not maximal (with respect to $<_i$) amongst the vertices that support $p$.
\end{lem}
\begin{proof}
Suppose for contradiction that we have $i \in [n]$ and $p \in \cP$ such that $I_i(p)$ is $<_i$-maximal in $V(p)$. There are two possibilities, which are illustrated in Figure~\ref{fig:no fourth vertex}: \st{either $p = (i-1,b)$ for some $b$ (so $i$ and $I_i(p) = i-1$ are the two ends of a single edge), or $p = (a,b)$ with $i\leq_i a <_i b$ and $I_i(p) = b+1$.} {\color{violet}either $i-1 \in V(p)$, in which case it is the last vertex in the $<_i$ order and $I_i(p)= i-1$, or $i-1 \not \in V(p)$ in which case,  $p= a, b$, $i \in [b+2, a]$ and $I_i(p) = b+1$.}

@@

So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $\big|[a+1,b]\big|$ is minimal amongst propagators of $W$ with this property. \sanote{in the picture for case 2, $\big|[d+1,b]\big| <\big|[a+1,b]\big|$.Worried about case 2}

@@

\begin{cor}\label{GN alg well defined}
If $W$ is an admissible Wilson loop diagram with $k$ propagators, then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ distinct vertices to each $I_i$.
\end{cor}
\begin{proof}
Fix $i \in [n]$. It follows from the proof of Lemma~\ref{lem no fourth vertex} that in applying Algorithm~\ref{alg:put GN on WLD} to construct the set $I_i$, the algorithm can never reach the fourth vertex of a propagator's support (ordered with respect to $<_i$) without having already assigned that propagator. Therefore if the algorithm starts at vertex $i$, all propagators must have been eliminated by the time it gets to vertex $i-1$, ensuring that the algorithm is completed in less than one full circumnavigation of the diagram and that $I_i$ contains exactly $k$ distinct elements.
\end{proof}

@@

Let $W = (\cP,[n])$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.  Then $J_p^{W}(i)$, $J_p^{W}(i+1)$, $J_p^{W}(j)$, and $J_p^{W}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
\end{lem}

@@

In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation). Note that this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary. Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}). $V$ is guaranteed to be an admissible diagram, since it was formed by removing a propagator from a diagram that was at least weakly admissible.

@@

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. Note that $p$ has no effect on other propagators for starting vertices in this range, so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ is assigned to a vertex, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in Case 2 of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

@@

  \begin{equation}\label{eq necklace}
  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\text{ in}}]{} I_{n-1}^{V} \xrightarrow[\substack{n-1\text{ out}\\\text{something in}}]{} I_{n}^{V}  \xrightarrow[\substack{n \text{ out}\\\text{something in}}]{} I_1^{V}
  \end{equation}
  where the first ``something'' is either $n$ or an element of $I_1^{V}$, and the second ``something'' is an element of $I_1^{V}$.

  \begin{figure}
    \[\includegraphics{messy}\]
    \caption{Plusses coming from $I_{n-2}^{V}$ (top left), $I_{n-1}^{V}$ (top right), and $I_n^V$ (bottom row), in the case where ${n-1, n-2\in I_{n-2}^{V}}$.  The blue lines are the non-intersecting paths defining the position of the plusses.  The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
  \end{figure}

  Using this information we can determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$.  Note that $I_{n-2}^V\setminus I_1^V$ and $I_1^V\setminus I_{n-2}^V$ each have size $\leq 3$ by the definition of a Grassmann necklace. We have $n-1, n-2 \in I_{n-2}^{V} \setminus I_1^V$ for certain, and the third element (if it exists) must be $n$. On the other hand we have $n-5 \in I_1^{V} \setminus I_{n-2}^V$, along with at least one and at most two other elements.  If there is one such element, call it $a$.  If there are two, call them $a$ and $b$ with $a>b$.

  This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the top left diagram in Figure~\ref{fig messy}.  Stepping to $I_{n-1}^{V}$ simply removes the $(n-5)\rightarrow (n-2)$ path (top right diagram of Figure~\ref{fig messy}), so $I_{n-1}^V$ contributes no new information about the Le diagram of $V$.

  %Stepping to $I_{n}^{V}$, $n-1$ is removed and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence is no longer available as the starting point for a path.  This gives two possible configurations illustrated in the bottom two parts of Figure~\ref{fig messy}.

  With this information in hand, we can now tackle the points in the statement of the lemma. We know that 
  \[I_{n-2}^{W}  = (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}, \quad n-5 \in I_1^W, \quad n-3\not\in I_{n-2}^W,\]
 and so the paths for building plusses from $I_{n-2}^{W}$ start at
 \[I_1^W \setminus I_{n-2}^W = \{n-3,n-5\} \cup (I_1^V \setminus I_n^V)\]
 and end at
 \[I_{n-2}^W \setminus I_1^W = \{n-2,n-1\}\cup(I_n^V \setminus I_1^V).\]
This means that $I_{n-2}^W$ contributes plusses as in Figure~\ref{fig messyD}, while $I_n^V$ contributes as in the bottom line of Figure~\ref{fig messy}, which proves point (1) and most of point (3). From equation \eqref{eq necklace} we see that $n-2$ appears only in $I_{n-2}^V$, so no other Grassmann necklace term for $V$ can contribute a plus in the $n-2$ column; this completes the proof of item (3).

  \begin{figure}
     \[\includegraphics{messyD}\]
    \caption{Plusses coming from $I_{n-2}^{W}$.}\label{fig messyD}
  \end{figure}

Now consider $I_{n-3}^{V}$.  By equation~\eqref{eq necklace} $I_{n-3}^{V}$ contributes almost the same plusses as $I_{n-2}^{V}$: the only difference is that it contributes an $(n-5)\rightarrow (n-3)$ plus in place of the $(n-5)\rightarrow (n-2)$ plus.  Since we must have $n-3\in I_{n-3}^{V}$ (because the propagator $q$ exists in $V$), it follows from Lemma~\ref{lem I} that $I_{n-3}^{W} = I_{n-3}^{V}\cup\{n-2\}$.  Thus the paths for $I^{W}_{n-3}$ are the same as those for $I^{V}_{n-3}$ except that the path that did go to $n-3$ now goes to $n-2$.  This cannot conflict with another path since equation~\eqref{eq necklace} shows that $n-2$ only appears in $I_{n-2}^{V}$ among the necklace elements of $V$.

This proves point (2), and combined with the observation above that $I_{n-1}^V$ contributes no new plusses compared to $I_{n-2}^V$, we also obtain item (4).

  Finally, if the Le diagram of $V$ did admit a $(n-5)\rightarrow (n-1)$ plus, it could only have been contributed by a necklace term that doesn't contain $n-5$.  By equation \eqref{eq necklace} the only terms that could have this property are $I_{n-2}^{V}$, $I_{n-3}^{V}$, and $I_{n-4}^{V}$, and the analysis above shows that $I_{n-2}^V$ and $I_{n-3}^V$ do not contribute a plus in this position.

  Recall that $n-5$ is the largest row index in the Le diagram of $V$, and $n-5 \in I_1^V \setminus I_{n-4}^V$ so $I_{n-4}^V$ must contribute a path starting at $n-5$. Since $n-4 \in I_{n-4}^V$ by the location of the propagator $q$, we must also have a path ending at $n-4$. Since the paths cannot cross, this implies that $I_{n-4}^V$ must contribute a $(n-5) \rightarrow (n-4)$ plus, and hence cannot contribute a $(n-5)\rightarrow (n-1)$ plus. This proves point (5) and completes the proof of the lemma.
\end{proof}

\begin{lem}\label{lem other k}
  Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that if $n-2\in I_{n-2}^{V}$ then $n-1\in I_{n-2}^{V}$ also. Then for each $k$ in the range $1<k<n-2$, $I_k^{W}$ contributes the same plusses as $I_{k}^{V}$, except that if $I_{k}^{V}$ contributed a plus in the $n-3$ column of the Le diagram of $V$ then this plus is shifted one square left in the Le diagram of $W$, and no plus was already in that location in the Le diagram of $W$.
\end{lem}

\begin{proof}
Recall that $I_1^W = I_1^V\cup \{n-3\}$ and that $n-2,n-1,n \not\in I_1^W$.

  If $n-3\not\in I_{k}^{V}$ then by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-3\}$.  Then since $n-3$ is the largest element of $I_1^{W}$ this transformation leaves the disjoint paths unchanged and so the plusses carry over from $V$ to $W$ directly.

  If $n-3\in I_{k}^{V}$ then $I_k^V$ must contribute a plus in the $n-3$ column of the Le diagram of $V$, and by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-2\}$. If $n-2$ supports no propagators in $V$ then certainly no plusses appear in the $n-2$ column of the Le diagram of $V$. If $n-2$ supports at least one propagator in $V$ then $n-2 \in I_{n-2}^V$ and so by hypothesis $n-1 \in I_{n-2}^V$ as well. By Lemma~\ref{lem n-2 bad}, the only necklace element of $V$ containing $n-2$ is $I_{n-2}^{V}$ and the corresponding plus is not contributed to the Le diagram of $W$ by $I_{n-2}^{W}$.

  Since $n-3 \in I_k^V \setminus I_1^V$, we must have a path in the Le diagram of $V$ from some vertical edge $i$ to the bottom edge $n-3$.  In the Le diagram of $W$, the index $n-3$ labels a vertical edge with no path starting at it (since $n-3$ belongs to both $I_1^W$ and $I_k^W$), and there must be a path leading to $n-2$ since $n-2 \in I_k^W \setminus I_1^W$.  By the previous paragraph no other path from $I_k^V$ could end at $n-2$, and since the paths cannot cross we conclude that the $i\rightarrow (n-3)$ path in the Le diagram of $V$ must become a $i\rightarrow (n-2)$ path in the Le diagram of $W$. All other paths are unchanged.

   Thus the plus contributed by $I_k^V$ in the $n-3$ column of the Le diagram of $V$ is shifted into the $n-2$ column in the Le diagram for $W$, where there was no plus before, and no other plusses are changed.
\end{proof}

We are now ready to prove the main result of this section, showing that the dimension of the positroid cell associated to each Wilson loop diagram is $3|\cP|$.

\begin{thm}\label{thm dim}
  The number of plusses in the Le diagram of an admissible Wilson loop diagram is three times the number of propagators.
\end{thm}

\begin{proof}
  The proof is by induction on the number of propagators.

  First note that a Wilson loop diagram $W$ with one propagator supported on vertices $i<j<k<\ell$ has Le diagram a single row with $|W|-i$ boxes.  Labelling the columns from left to right by $|W|, \ldots, |W|-i+1$, by Algorithm~\ref{alg:GN to Le} there are plusses in the $j$, $k$, and $\ell$ positions.

  Now consider Wilson loop diagrams with $k>1$ propagators.  By Lemma~\ref{lem uncovered} it suffices to prove the result for weakly admissible Wilson loop diagrams with $k$ propagators and no non-supporting vertices.  By Lemma~\ref{lem dihedral} it suffices to prove the result for at least one Wilson loop diagram from each dihedral orbit.  Take a weakly admissible Wilson loop diagram $W$ with $k$ propagators and no non-supporting vertices.  Make a dihedral transformation of $W$ if necessary so that $W$ has a propagator $p$ with the properties in Lemma~\ref{lem good p}.

  We make one further simplification: if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports only $p$ but $n-2$ supports at least one other propagator, then flip $W$ on the line perpendicular to the $(n-2){th}$ edge to obtain a diagram with the configuration of Case 1. This eliminates the possibility that we could have $n-2 \in I_{n-2}^W$ but $n-1 \not\in I_{n-2}^W$.

  This diagram will be our $W$ for the remainder of the proof. Let $V$ be $W$ with $p$ removed.

  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described in that lemma and subsequent discussion.  Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.  Lemmas~\ref{lem n and n-1} through \ref{lem other k} show that there is a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.  This bijection can be described as follows:
  \begin{itemize}
  \item All plusses from $\mathcal{B}$ for $V$ maintain their positions in $\mathcal{B}$ for $W$.
  \item All plusses from the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ maintain their positions in $\mathcal{A}$ for $W$.
  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus.  This plus is mapped to the $(n-5)\rightarrow (n-1)$ plus for $W$.
  \item All plusses in the $n-3$ column for $V$ are shifted one square to the left in $\mathcal{A}$ for $W$, i.e. into the $n-2$ column.
  \end{itemize}
  Note that this map is reversible and hence bijective. Indeed, the only possible ambiguity is at the $(n-5)\rightarrow (n-1)$ plus in $W$ (if it exists), which could have come from either of the first or third bullet points. However, if the third bullet point applies then by Lemma~\ref{lem n-2 bad} there is no $(n-5)\rightarrow (n-1)$ plus in $V$, i.e. the first bullet point does not apply.

  % If the Le diagram for $V$ has a plus in the $n-2$ column then Lemma~\ref{lem n-2 bad} applies. By the final part of Lemma~\ref{lem n-2 bad} there is no $n-5\rightarrow n-1$ plus in the Le diagram of $V$, and so the $n-5\rightarrow n-1$ plus of $W$ can be uniquely mapped to the plus in the $n-2$ column of the Le diagram of $V$.  If the Le diagram for $V$ has no plus in the $n-2$ column, then leave the $n-5\rightarrow n-1$ plus where it is in moving back to $V$.  This reverses the map.

Therefore the Le diagram of $W$ contains $3(k-1)$ plusses in bijection with the plusses from the Le diagram of $V$ and 3 new plusses in the bottom row, yielding $3k$ in total. Applying induction completes the proof.
\end{proof}

\section{Poles of Wilson Loop Integrals}\label{sec poles}

In this section, we investigate the poles of the integrand for $I(W)$, that is $R(W)$ as defined in Definition~\ref{def R(W)}. It is conjectured that for a fixed number of propagators and a given set of external twistors $\cZ$, [cite]\note{A cite still waiting} \bas \sum_{W | |\cP| = k} I(W)(\cZ) <\infty \;.\eas In otherwords, all poles of the intergrals must cancel. As a step towards this, in this section, we prove some results about $R(W)$.

The results of Section~\ref{sec GN algorithm} allow us to relate the position of propagators in a Wilson loop diagram $W$ to minors of $C(W)$, $R(W)$.

The main result of this section is Theorem~\ref{thm denom}, which expresses the denominator $R(W)$ in terms of the Grassmann necklace of $W$. This simplifies the computation of $R(W)$ and allows us to directly relate the poles of the integral to the combinatorics of the diagram.

We first give an algorithm which extracts the required minors from the Grassmann necklace.

\begin{algorithm}\label{alg WLD to denom via GN}
Let $W = (\cP,n)$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} with a fixed ordering on $\cP$. (see Section~\ref{section WLD background}).
\begin{itemize}
  \item For each $i \in [n]$, we construct a factor $r_i$ as follows:
    \begin{itemize}
      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.  (By convention set $I_{0}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.  Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
      \item Let $S_i = \{p \in \cP \ | \ I_{i-1}(p) \neq I_i(p)\}$. (By convention, set $I_{0} = I_n$.)
	  %\item Write $\Delta_{I_i}$ for the determinant of the $k \times k$ minor of $C(W)$ with columns indexed by $I_i$.
      \item Let $r_i$ be the determinant of the $|S_i|\times |S_i|$ minor of $C(W)$ with rows indexed by $S_i$ and columns indexed by $I_i(S_i)$.  %$\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
    \end{itemize}
  \item Define $R = \prod_{i=1}^n r_i$.
\end{itemize}
\end{algorithm}

That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $i-1^{st}$.

As we discuss the algorithm it will also be useful to have the notation $\Delta_{I_i}$ for the determinant of the $k\times k$ minor of $C(W)$ with columns indexed by $I_i$.

As we take each $r_i$ to simply be the determinant of a particular submatrix of $C(W)$, the sign of each $r_i$ is well-defined.  Before proving the main results of this section, we given an illustrative example. Below, we show that $R$ is equal to the denominator of the Wilson loop diagram as defined in Definition~\ref{def R(W)}, and is the radical of the product $\prod_{i=1}^n \Delta_{I_i}$.
%  However, we will not be interested in these signs as they only contribute an overall sign to $R$ and our main theorem in this section (Theorem~\ref{thm denom}) will simply be to show that $R$ is equal up to a $\mathbb{Q}$-multiple to the denominator of the Wilson loop diagram (see Definition~\ref{def R(W)}).

\note{I would like to discuss the angles of the arrows in fig 14}
\begin{tabular}{rrrrr}
\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\drawWLD{7}{1.5}
	\drawnumbers
	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}
	\drawlabeledprop{1}{1}{4}{0}{\footnotesize \; \qquad  $s$}
	\pgfmathsetmacro{\move}{\angle/\n};
	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + -1*\move:\radius) to[bend left = 45] (\angle*1:\radius); %p
	\draw[->,shorten >=2pt,red,thick] (1.5*\angle:\radius) to[bend right = 45] (\angle*2:\radius); %q
	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend left = 45] (\angle*4:\radius); %r
	\node at (\angle*1.5:\radius*2) {$I_1$};
	\node[align = center] at (4*\angle:\radius*1.7) {$I_1(p) = 1, \; I_1(q) = 2,$ \\[5pt] $I_1(s) = 4$.};
	& \quad \quad  &
\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\drawWLD{7}{1.5}
	\drawnumbers
	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}
	\drawlabeledprop{1}{1}{4}{0}{\footnotesize \; \qquad  $s$}
	\pgfmathsetmacro{\move}{\angle/\n};
	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + -1*\move:\radius) to[bend right = 45] (\angle*2:\radius); %p
	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend left = 45] (\angle*5:\radius); %q
	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend left = 45] (\angle*4:\radius); %r
	\node at (\angle*1.5:\radius*2) {$I_2$};
	\node[align = center] at (4*\angle:\radius*1.7) {$I_2(p) = 1,  \; I_2(s) = 4,$ \\[5pt] $I_2(q) = 5.$};
& \quad & 
\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\drawWLD{7}{1.5}
	\drawnumbers
	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}
	\drawlabeledprop{1}{1}{4}{0}{\footnotesize \; \qquad  $s$}
	\pgfmathsetmacro{\move}{\angle/\n};
	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend left = 45] (\angle*6:\radius); %p
	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend left = 45] (\angle*5:\radius); %q
	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend left = 45] (\angle*4:\radius); %r
	\node at (\angle*1.5:\radius*2) {$I_3 = I_4$};
	\node[align = center] at (4*\angle:\radius*1.7) {$I_3(s) = 4,\;  I_3(q) = 5,$ \\[5pt] $I_3(p) = 6.$ };
 & & & &  \\
 \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\drawWLD{7}{1.5}
	\drawnumbers
	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}
	\drawlabeledprop{1}{1}{4}{0}{\footnotesize \; \qquad  $s$}
	\pgfmathsetmacro{\move}{\angle/\n};
	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend right = 45] (\angle*7:\radius); %p
	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend right = 45] (\angle*6:\radius); %q
	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend right = 45] (\angle*5:\radius); %r
	\node at (\angle*1.5:\radius*2) {$I_5$};
	\node[align = center] at (4*\angle:\radius*1.7) {$I_5(s) = 5,\;  I_5(q) = 6,$  \\[5pt] $I_5(p) = 7$ };
& \quad & 
\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\drawWLD{7}{1.5}
	\drawnumbers
	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}

>>>>

Since each propagator is removed by the algorithm after it contributes, each propagator contributed exactly once to $I_i$, making the above ordering well defined.
Note that different $I_*$ impose different orderings on the propagators. Furthermore, Corrollary \ref{GN alg well defined} shows that this ordering respects the ordering of vertices in $I_i$. That is, $I_i(p_j) <_i I_i(p_l)$ for all $j <l$.

@@

\begin{rmk} \label{clockwise ordering rem}
When $p$ contributes $I_i(p) = a$, it must be the clockwise-most propagator amongst those not yet assigned that is supported on $a$ i.e. any propagator assigned later that is supported on $a$ must be inside $(p, <_{a-1})$.
\end{rmk}

@@

With this setup, if we can find a vertex $\ell$ (with \hlfix{$\ell <_i i$ and $\ell <_m m$}{ $i <_i \ell$ and $m <_m \ell$? This is what is in the picture?}) such that the \emph{configuration} of propagators ending in the interval \st{$(j-1, \ldots, \ell+1)$} {\color{violet}$[j, \ell]$} is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive). See Figure~\ref{fig:locally identical} for an illustration of this.

@@

With that in mind, we are ready to begin proving properties of the algorithm. We first show that the algorithm for $I_i$ can never reach the final vertex (in the $<_i$ order) in a propagator's support without having already assigned that propagator; in particular, this guarantees that the construction of $I_i$ always terminates in fewer than $n$ steps, as shown in Corrollary \ref{GN alg well defined}.

\begin{lem}\label{lem no fourth vertex}
Let $W$ be an admissible Wilson loop diagram containing at least one propagator. For any $i \in [n]$ and for any $p \in \cP$, $I_i(p)$ is not maximal (with respect to $<_i$) amongst the vertices that support $p$.
\end{lem} \sanote{wanted to rewrite this lemma to emphasize the fact that we are using the same properties of Alg 3.7 over and over again, and have these principals set apart in a remark}
\begin{proof}
Suppose for contradiction that we have $i \in [n]$ and $p \in \cP$ such that $I_i(p)$ is $<_i$-maximal in $V(p)$. There are two possibilities, which are illustrated in Figure~\ref{fig:no fourth vertex}: \st{either $p = (i-1,b)$ for some $b$ (so $i$ and $I_i(p) = i-1$ are the two ends of a single edge), or $p = (a,b)$ with $i\leq_i a <_i b$ and $I_i(p) = b+1$.} {\color{violet}either $i-1 \in V(p)$, in which case it is the last vertex in the $<_i$ order and $I_i(p)= i-1$, or $i-1 \not \in V(p)$ in which case,  $p= a, b$, $i \in [b+2, a]$ and $I_i(p) = b+1$.}

@@

So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $\big|[a+1,b]\big|$ is \hlfix{minimal amongst propagators of $W$ contributing their last vertices with this property.}{changed wording to be accurate, but feels clunky}

@@

\begin{cor}\label{GN alg well defined}
If $W$ is an admissible Wilson loop diagram with $k$ propagators and $n$ vertices. Then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ distinct vertices to each $I_i$ in $n$ steps.
\end{cor} 
\begin{proof}
Fix $i \in [n]$. It follows from the proof of Lemma~\ref{lem no fourth vertex} that in applying Algorithm~\ref{alg:put GN on WLD} to construct the set $I_i$, the algorithm can never reach the fourth vertex of a propagator's support (ordered with respect to $<_i$) without having already assigned that propagator. Therefore if the algorithm starts at vertex $i$, all propagators must have been eliminated by the time it gets to vertex $i-1$, ensuring that the algorithm is completed in less than one full circumnavigation of the diagram and that $I_i$ contains exactly $k$ distinct elements.
\end{proof}

@@

Let $W = (\cP,[n])$ be an admissible Wilson loop diagram\st{, and}{\color{violet}. For every }$p = (i,j) \in \cP$\st{.  Then}{\color{violet}, the sets} $J_p^{W}(i)$, $J_p^{W}(i+1)$, $J_p^{W}(j)$, and $J_p^{W}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
\end{lem}

@@

In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies \hlfix{the statement of the theorem by the induction hypothesis}{??? changed to statement of the theorem slightly to make this make sense}, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation). Note that this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary. Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}). $V$ is guaranteed to be an admissible diagram, since it was formed by removing a propagator from a diagram that was at least weakly admissible.

@@

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. \hlfix{Note that $p$ has no effect on other propagators for starting vertices in this range,}{By rmk \ref{rmk algorithm locally same}?} so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ \st{is assigned to}{\color{violet}contributes}\sanote{has this changed emphasis too much?} a vertex, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in Case 2 of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

@@

  \begin{equation}\label{eq necklace}
  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\
